# Results {#sec-results}

```{r}
#| label: results-setup
#| include: false
source("scripts/analysis.R")
```

## Descriptive statistics

The dataset contains `r nrow(x)` observations. Mean speed is `r round(mean(x$speed), 2)` mph, and mean stopping distance is `r round(mean(x$dist), 2)` ft.

```{r}
#| label: tbl-summary
#| tbl-cap: "Descriptive statistics for speed and stopping distance"
knitr::kable(data.frame(
  Variable = c("Speed (mph)", "Stopping distance (ft)"),
  Mean = c(mean(x$speed), mean(x$dist)),
  SD = c(sd(x$speed), sd(x$dist))
), digits = 2, booktabs = TRUE)
```

@tbl-summary presents the mean and standard deviation of both variables.

## Speed and stopping distance

```{r}
#| label: fig-cars
#| fig-cap: "Speed and stopping distance"
#| fig-width: 5
#| fig-height: 3.5
plot(x$speed, x$dist, pch = 19, col = "#333333",
     xlab = "Speed (mph)", ylab = "Stopping distance (ft)")
abline(model, col = "#333333", lwd = 2)
```

@fig-cars shows that stopping distance tends to increase with speed. The estimated slope is `r round(coef(model)[2], 2)`. These results illustrate the template and are not findings from an actual thesis.
